\documentclass[twoside]{article}
\usepackage[]{dylan} % put copy for copyright, serif for serif font, utopia for utopia font, and hide to get rid of hints and small solutions
 
\renewcommand{\abstractname}{\large\sffamily\bfseries\color{DylanBlue}Summary}
 
\title{Example File with dylan.sty}
\author{Dylan Yu}
\date{\today}
\runningheads{\textbf{Dylan Yu} (\today)}{Example File with dylan.sty}
 
\begin{document}
\maketitle

\begin{abstract}
Summarize what you are going to teach here. For example, today's topic is how to use \verb|dylan.sty|. Yay! I am writing more things to fill up the summary so you can see what it looks like.
\end{abstract}

\tableofcontents
\newpage

\section{Test}
\subsection{Testing}
\subsubsection{Tested}
\begin{defn}[Definition]
The word \vocab{definition} refers to the meaning of something.
\end{defn}
\begin{theorem}
Theorems, lemmas, corollaries, postulates, and propositions are all defined together. 
\end{theorem}
\begin{lemma}[Title of Lemma]
You can title all of these as well.
\end{lemma}
\begin{corollary}

\end{corollary}
\begin{postulate}

\end{postulate}
\begin{prop}

\end{prop}
\begin{proof}
We will use the following lemma:
\begin{lemma*}
This lemma is not numbered. Some unnumbered theorem styles are undefined, so create your own if necessary.
\end{lemma*}
\end{proof}
\begin{example}

\end{example}
\begin{soln}

\end{soln}
\begin{problem}

\end{problem}
\begin{walk}
Explains the problem through steps:
\begin{enumerate}
    \item Read the problem.
    \item Read the problem again.
    \item Got it?
\end{enumerate}
\end{walk}

\begin{moral}
Use Dylan's .sty!
\end{moral}

\begin{fact}

\end{fact}

\begin{remark}

\end{remark}

\begin{basecase}

\end{basecase}

\begin{indstep}

\end{indstep}

\begin{case}

\end{case}

\begin{boxpar}[Paragraph Title]
Paragraphs are cool. This is a paragraph. It is very interesting. It even repeats! Replacing this with words you want will make the paragraph even better. Try it out! Paragraphs are cool. This is a paragraph. It is very interesting. It even repeats! Replacing this with words you want will make the paragraph even better. Try it out! Paragraphs are cool. This is a paragraph. It is very interesting. It even repeats! Replacing this with words you want will make the paragraph even better. Try it out!
\end{boxpar}

\begin{exercisebox}
\begin{exercise}
Consider $\triangle ABC$ with incenter $I.$ Prove that $\angle BIC=90^{\circ}+\frac{1}{2}\angle BAC.$
\end{exercise}
\begin{exercise}
If $1+1=3$, what is $2+2$?
\begin{hint}
\begin{addhint}
{This is a hint.}
\end{addhint}
\begin{addhint}
{You can add multiple hints.}
\end{addhint}
\end{hint}
\begin{sol}
\begin{addsol}
{You can also add solutions.}
\end{addsol}
\end{sol}
\end{exercise}
\begin{exercise}[Not a real problem]
How many beans are in my pocket?
\end{exercise}
\begin{exercise}
Exercise boxes can even go across pages!\footnote{This is a footnote.}
\end{exercise}
\end{exercisebox}

\appendix % this makes the sections A,B,C,etc.
\input{hint}
\input{sol}

\end{document}
